Discrete Quantum Theories and Computing

### 2018-04-09 dissertation.tex
dissertation.lyx Chapter 1 Introduction Updating...

analog computing and probabilistic computing

>>>>

When we check the compatibility between quantum mechanics and computer
science, we found their fundamental assumptions are different. On
one hand, quantum mechanics is based on infinitely precise real and
complex numbers. On the other hand, current computers perform discrete
computation most of the time, except some analog chips communicating
with physical world~\cite{Camenzind2005}. While analog chips in
theory could manipulate infinitely precise real numbers, their computability
in practice is far weaker than the prediction of real computation
\cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
One of the reason behind this gap is that our measurement precision
is always finite, and the same reason might also limit the computability
of a realistic quantum computer. To understand these problems, we
tried two different approaches. We first tried to build discrete quantum
theories and computing by considering quantum theories and computing
over finite fields in Chapter~\ref{chap:DQT=000026DQC}. We then
tried to incorporate the idea of finite precision measurement with
quantum theories in Chapter~\ref{chap:QIVPM}.
